---
title: "DS 3001 Text Mining Lab"
author: "Group 10"
date: "3/24/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages=FALSE, errors=FALSE)
```


```{r, include=FALSE}
library(tidyverse)
library(tidytext)
library(textdata)
# install.packages("tidyselect")
library(tidyselect)
library(stringr)
library(DT)
# install.packages("topicmodels")
library(tm)
library(plotly)
library(topicmodels)
# save.image("innovedu.RData")
```


# Problem Statement
Congratulations you've successfully transferred from being a NBA 'quant' scout to a consultant specializing in US national sentiment! You've been hired by a non-profit in secret to track the level of support nationally and regionally for the field of Data Science. The goal is to get a general idea of patterns associated with articles being written on the broad topic of Data Science (you can also choose to select a sub-topic). In doing so your data science team has decided to explore periodicals from around the country in a effort to track the relative positive or negative sentiment and word frequencies. Luckily your team has access to a world class library search engine call LexusNexus (NexusUni) that provides access to newspapers from around the country dating back decades. You'll first need to decided what words you want to track and what time might be interesting to begin your search. 

You'll need to select several newspapers from different regions in the country limiting the search to 100 articles from each paper, run sentiment analysis with each newspaper serving as a corpus and then compare the level of positive or negative connotation associated with the outcomes. Also, run tf-idf on each corpus (newspapers) and work to compare the differences between the distributions (5 to 6 newspapers should be fine)

Your main goal (and the goal of all practicing data scientists!) is to translate this information into action. What patterns do you see, why do you believe this to be the case? What additional information might you want? Be as specific as possible, but keep in mind this is an initial exploratory effort...more analysis might be needed...but the result can and should advise the next steps you present to the firm. 


Please submit a cleanly knitted HTML file describing in detail the steps you took along the way, the results of your analysis and most importantly the implications/next steps you would recommend.  You will report your final results and recommendations next week in class. This will be 5 minutes per group. 

You will need also need to try to collaborate within your group via a GitHub repo, if you choose it would be fine to assign 1 or 2 regions/newspapers per group member, that can then be added to the repo. Create a main repo, everyone should work in this repo and submit independently using branching/pull requests. If you want to try to use pull request to combine everyone's work into a final project, please do so, but it's not a requirement. Select a repo owner that sets up access (push access) for the week, we will rotate owners next week. Also, submit a link to your the GitHub repo (every group member can submit the same link). 

Create collaborations in GitHub: https://docs.github.com/en/github/collaborating-with-issues-and-pull-requests/about-collaborative-development-models

Rstudio Guidance on Git and Github (Including Branching/Pull Requests): https://r-pkgs.org/git.html#git-branch


Here is the link to the database search via the UVA Library that should lead you to LexusNexus (Now Nexas Uni)
https://guides.lib.virginia.edu/az.php?a=l

# Group Work{.tabset}

## Joseph's Section

I have chosen to work on newspapers from the midwest of the United States

### Choose Newspapers

Telegraph Herald - Iowa

The Daily Oklahoman - Oklahoma

### Choose Articles

Articles were chosen from the two Newspapers, all that were available were used

### Get the data
```{r}

# read in the raw data
docs_1 <- read_lines("mid_west_file_1_1.rtf")

# put the data into a tibble
docs_1 <- tibble(docs_1)

# here will still have the {} symbols and a lot of giberish

# remove all the info contained in {} and some giberish
docs_1 <- docs_1 %>%
  unnest_tokens(word, docs_1) 

# remove unimportant words
docs_1 = docs_1 %>% 
  anti_join(stop_words) 

# find the count of each word
docs_1 = docs_1 %>%
  count(word, sort = TRUE)

docs_1 <- docs_1 %>% 
  filter(!grepl("[[:digit:]]", word)) 

docs_1 <- docs_1 %>%
  filter(!str_detect(word, "na"))

view(docs_1)
```

```{r}
# read in the raw data
docs_2 <- read_lines("mid_west_file_2_1.rtf")

# put the data into a tibble
docs_2 <- tibble(docs_2)

# here will still have the {} symbols and a lot of giberish

# remove all the info contained in {} and some giberish
docs_2 <- docs_2 %>%
  unnest_tokens(word, docs_2) 

# remove unimportant words
docs_2 = docs_2 %>% 
  anti_join(stop_words) 

# find the count of each word
docs_2 = docs_2 %>%
  count(word, sort = TRUE)

docs_2 <- docs_2 %>% 
  filter(!grepl("[[:digit:]]", word)) 

docs_2 <- docs_2 %>%
  filter(!str_detect(word, "na"))

view(docs_2)
```


### Process the data
This section does not work, unnest_tokens is not working inside the function
```{r}

process_rtf = function(file_name){
  
  rtf_result = read_lines(file_name)
  
  rtf_tibble = tibble(rtf_result) %>%
    mutate(rtf_result = as.character(rtf_result))
  
  # remove all the info contained in {} and some giberish
  rtf_tibble <- rtf_tibble %>%
    unnest_tokens(word, rtf_result) 
  
  # remove unimportant words
  rtf_tibble = rtf_tibble %>% 
    anti_join(stop_words) 
  
  # find the count of each word
  rtf_tibble = rtf_tibble %>%
    count(word, sort = TRUE)
  
  rtf_tibble <- rtf_tibble %>% 
    filter(!grepl("[[:digit:]]", word)) 
  
  rtf_tibble <- rtf_tibble %>%
    filter(!str_detect(word, "na"))
  
  return(rtf_tibble)

}

file_name="mid_west_file_1_1.rtf"

a = process_rtf(file_name)

```


```{r}
combined = rbind(docs_1, docs_2) %>%
  group_by(word) %>%
  summarize(n=sum(n)) %>%
  arrange(-n)

combined
```


### Sentiment Analysis
```{r}
# load sentiment data
get_sentiments('afinn')
get_sentiments('nrc')
get_sentiments('bing')
```
```{r}
combined_afinn = combined %>%
  inner_join(get_sentiments("afinn"))
combined_nrc = combined %>%
  inner_join(get_sentiments("nrc"))
combined_bing = combined %>%
  inner_join(get_sentiments("bing"))
```

### Plots
```{r}

afinn_to_histogram_data = function(afinn_data){
  temp = afinn_data %>%
    group_by(value)%>%
    summarize(n=n())
  
  return(temp)
}

afinn_plot = function(afinn_data){
  plt = afinn_data %>%
    ggplot(
      aes(
        x=value,
        y=n,
        fill=n
      )
    )+
    geom_bar(
      stat='identity'
    )+
    geom_smooth(
      method='loess',
      se=F,
      formula='y~x'
    )
  
  return(plt)
}

plt = combined_afinn %>%
  afinn_to_histogram_data() %>%
  afinn_plot()

plt
```

```{r}

afinn_cloud_plot = function(afinn_data){
  plt = afinn_data %>%
  head(50) %>%
  ggplot(
    aes(
      label=word,
      size=n
    )
  )+
  geom_text_wordcloud(
  )+
  theme_minimal()
  
  return(plt)
}

afinn_cloud_plot(combined_afinn)
```


```{r}

west_afinn = combined_afinn

east_afinn = combined_afinn

all_regions_afinn = rbind(west_afinn %>% mutate(region='west'), east_afinn %>% mutate(region='east'))


west_afinn_hist_data = west_afinn %>%
  afinn_to_histogram_data()%>%
  mutate(region='west')

east_afinn_hist_data = east_afinn %>%
  afinn_to_histogram_data()%>%
  mutate(region='east')

all_regions_hist_data = rbind(west_afinn_hist_data, east_afinn_hist_data)


```


```{r}
all_regions_hist_data %>%
  afinn_plot() +
  facet_wrap(
    .~region
  )
```


```{r}
all_regions_afinn %>%
  afinn_cloud_plot(
  )+
  facet_wrap(
    .~region
  )
```



```{r}
all_regions %>%
  ggplot(
    aes(
      x=value
    )
  )+
  facet_wrap(
    .~region
  )+
  geom_density(
    stat='density'
  )
```



### TF and IDF Analysis
























